Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-12 ForegroundSimulations/ms.tex
Address Judd's comments, Sort reference order
From ea7bb98 (fgsim):
====================

In ms.tex,

(*) Incorporate comments from Judd
(*) Fix some math errors

In eor.bib,

(*) Sort Thyagarajan et al. (2015a,b)

%% \usepackage{ccaption}
%% \captionstyle{\raggedright}
\usepackage[caption=false]{subfig}
\usepackage{amsmath}
\usepackage{footnote}
\usepackage{url}
\bibpunct{(}{)}{;}{a}{}{,} 
\captionsetup{belowskip=12pt,aboveskip=4pt}
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\newcommand{\dif}{\mathrm{d}}
%% \renewcommand*{\thefootnote}{\fnsymbol{footnote}}

@@

Unaccounted systematics from foregrounds and instruments prevent present day experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR). In-depth understanding of these effects is critical for such experiments to succeed. We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR measurements. Increase in chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated upper limits on these reflections to prevent further EoR signal degradation. We use the Hydrogen Epoch of Reionization Array (HERA) as an example. Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not require removal of foregrounds. We also show that all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization. The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.

@@

This paper is organized as follows. \S\ref{sec:HERA} introduces the HERA instrument. A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}. \S\ref{sec:sim} describes foreground simulations including antenna beam pattern, all-sky foreground models and two independent EoR models. \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on reflections in the instrument. Lower limits on sensitivity of HERA under simple {\it foreground avoidance} criteria are demonstrated in \S\ref{sec:eor-sensitivity}. Our findings are summarized in \S\ref{sec:summary}.

@@

The delay spectrum has a close resemblance to cosmological H~{\sc i} spatial power spectrum and is defined as:
\begin{align}\label{eqn:delay-power-spectrum}
  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, \label{eqn:kprll-delay}
\end{align}
where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology, and following \citet{par14},
\begin{align}
  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f,
\end{align}
which is related to the cosmic volume probed by the instrument.

In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

@@

It was recently discovered that in wide-field measurements diffuse foreground emission from wide off-axis angles appear enhanced in the delay spectrum near the edges of the {\it foreground wedge} even on wide antenna spacings \citep{thy15a}. Called the {\it pitchfork} effect, this arises due to severe foreshortening of baseline vectors towards the horizon along joining the antenna pairs thereby enhancing their sensitivity to large scale structures in these directions. Since delay spectrum maps directions on the sky to delay bins, the emission from large scales near the horizon appears enhanced in delay bins near the horizon limits of the {\it foreground wedge}. Since these delay modes lie adjacent to those considered sensitive to the EoR signal, they cause a significant contamination of line-of-sight modes critical for EoR signal detection. These findings were confirmed in MWA observations \citep{thy15b}.

@@

For reference, we use two models of EoR. In the first, simulations of the H{\sc i} signal were created using the publicly available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}. The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts. The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$. The second EoR model is borrowed from the simulations described in detail in \citet{lid08}. Hereafter, we refer to these two as EoR models 1 and 2 respectively.

@@

The equation for delay spectrum describes the mapping between sky location of a foreground object and delay. The chromatic nature (variation with frequency) of the antenna power pattern results in a convolution of the geometrical mapping with the delay response of spectral chromaticity of the power pattern. We discuss the resulting spillover of foreground power beyond the horizon delay limits.

@@

Since our aim in this paper is to quantify foreground contamination and EoR sensitivity without employing any sophisticated {\it foreground removal} techniques, we turn out attention to {\it foreground avoidance} strategy that employs spectral weighting technique. In such a scheme, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}. For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
\begin{align}\label{eqn:Beff}
  \epsilon &= \frac{1}{B} \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f, \\
  \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
  % B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
\end{align}
where, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth. For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$. % Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.

@@

This is an enormous gain in sidelobe characteristics for a negligible loss of sensitivity relative to a simple {\it Blackman-Harris} weighting. This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds and the beam patterns and not by sidelobes from spectral weighting. In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.

In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky. In all these panels, the full-band spectrally weighted foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively. The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases. A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity as the beam is changed from the achromatic to the {\it Airy} to the chromatic simulated model. For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths. It is also noted that despite the extreme dynamic range of the employed spectral weighting function, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude. This signals that the foreground spillover shown are truly limited by intrinsic spectral features in the antenna beam patterns.

@@

It is clearly demonstrated that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$. Thus, the chromaticity of antenna beam needs to be carefully controlled in EoR experiments in order to not allow sensitive $k_\parallel$-modes to become inaccessible for EoR H{\sc i} signal detection.

It must be emphasized that such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern which is independent of the position-dependent geometric delays. As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam. We leave delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction-dependent and beam chromaticity-dependent effects to future work.

@@

One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument. \citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed. Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam. In this section, we provide cosmologically motivated upper limits on instrument systematics caused by these two types of reflections.

The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$-modes which are considered sensitive for EoR H{\sc i} signal detection. Equivalently, these delay shifts introduce ripples in the spectrum. The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the fringes, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for. Equivalently, in the Fourier domain these factors have a convolving effect. In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the baseline fringes are included.

We define the required attenuation on the reflected foreground power as the ratio: 
\begin{align}\label{eqn:attenuation}
  \Gamma_{k_\textrm{p}}(\tau) \geq \min_{|k_\parallel|>k_\textrm{p}}\left\{\frac{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)}{P_\textrm{H{\sc i}}(k_\parallel)}\right\}^{1/2},
\end{align}
where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr local sidereal time (LST) range and over both positive and negative $k_\parallel$-modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}). Equivalently, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$. For this analysis constraining reflections, we use EoR model 1 at 150~MHz ($z\approx 8.47$).

For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on a 14.6~m baseline in equation~\ref{eqn:attenuation}. Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted). These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections. In other words, it implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$ modes of interest.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Lower limit on attenuation of reflected foreground power (in dB) from dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted). This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model. When the attenuation on dish-feed reflections is higher than these limits (outside the shaded regions), EoR will be detectable in respective $k_\parallel$-modes despite these reflections.}
\label{fig:fg-reflections-achrmbeam}
\end{figure}

@@

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Lower limit on attenuation of reflected foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right). This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models. Regions excluding shaded regions indicate EoR will be detectable in respective $k_\parallel$-modes despite these reflections. Increase in beam chromaticity makes the requirement on attenuation more severe. For instance, $k_\parallel > 0.1\,h$~Mpc$^{-1}$ modes will be inaccessible with the simulated chromatic beam if these reflections are taken into account. However, for the same beam the instrument will have much higher tolerance despite these reflections if the modes of interest are $k_\parallel > 0.2\,h$~Mpc$^{-1}$. Due to lower chromaticity, an {\it Airy} beam offers more tolerance to reflections than the simulated chromatic beam.}
\label{fig:fg-reflections}
\end{figure*}

>>>>

%% \usepackage{ccaption}
%% \captionstyle{\raggedright}
\usepackage[caption=false]{subfig}
\usepackage{amsmath}
\usepackage{footnote}
\usepackage{url}
\bibpunct{(}{)}{;}{a}{}{,} 
\captionsetup{belowskip=12pt,aboveskip=4pt}
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\newcommand{\dif}{\mathrm{d}}
\newcommand{\bibsortorder}[1]{}
%% \renewcommand*{\thefootnote}{\fnsymbol{footnote}}

@@

Unaccounted systematics from foregrounds and instruments prevent current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR). In-depth understanding of these effects is critical for such experiments to succeed. We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR measurements. Increase in chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation. We use the Hydrogen Epoch of Reionization Array (HERA) as an example. Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not perform removal of foregrounds. We also show that all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line-of-sight $k$-modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization. The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.

@@

This paper is organized as follows. \S\ref{sec:HERA} introduces the HERA instrument. A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}. \S\ref{sec:sim} describes foreground simulations including antenna beam pattern, all-sky foreground models and two independent EoR models. \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on reflections in the instrument. Foreground-limited sensitivity of HERA under simple {\it foreground avoidance} criteria are demonstrated in \S\ref{sec:eor-sensitivity}. Our findings are summarized in \S\ref{sec:summary}.

@@

The delay spectrum has a close resemblance to cosmological H~{\sc i} spatial power spectrum and is defined as:
\begin{align}\label{eqn:delay-power-spectrum}
  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, \label{eqn:kprll-delay}
\end{align}
where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest frame frequency of the 21~cm spin-flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. Following \citet{par14},
\begin{align}
  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f,
\end{align}
which is related to the cosmic volume probed by the instrument. In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

@@

It was recently discovered that in wide-field measurements diffuse foreground emission from wide off-axis angles appears enhanced in the delay spectrum near the edges of the {\it foreground wedge} even on wide antenna spacings \citep{thy15a}. Called the {\it pitchfork} effect, this arises due to severe foreshortening of baseline vectors towards the horizon along joining the antenna pairs thereby enhancing their sensitivity to large scale structures in these directions. Since delay spectrum maps directions on the sky to delay bins, the emission from large scales near the horizon appears enhanced in delay bins near the horizon limits of the {\it foreground wedge}. Since these delay modes lie adjacent to those considered sensitive to the EoR signal, they cause a significant contamination of line-of-sight modes critical for EoR signal detection. These findings were confirmed in MWA observations \citep{thy15b}.

@@

We use two models of EoR. In the first, simulations of the H{\sc i} signal were created using the publicly available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}. The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts. The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$. The second EoR model is from the simulations described in detail in \citet{lid08}. Hereafter, we refer to these two as EoR models 1 and 2 respectively.

@@

The equation for delay spectrum describes the mapping between sky location of a foreground object and delay. The chromatic nature (variation with frequency) of the antenna power pattern appears multiplicatively in the frequency axis and thus results in convolving its delay response with that of the foregrounds and the geometric phases measured by the baseline vector. We discuss the resulting spillover of foreground power beyond the horizon delay limits.

@@

Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique. In such a scheme, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}. For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
\begin{align}\label{eqn:Beff}
  \epsilon &= \frac{1}{B} \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f, \\
  \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
  % B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
\end{align}
where, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth. For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$. % Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.

@@

This is an enormous gain in sidelobe characteristics for a small loss of sensitivity relative to a simple {\it Blackman-Harris} weighting. This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds or beam patterns and not by sidelobes from spectral weighting. In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.

In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky. In all these panels, the full-band spectrally weighted foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively. The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases. A clear broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity as the beam is changed from the achromatic to the {\it Airy} to the chromatic simulated model. For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths. It is also noted that despite the extreme dynamic range of the spectral weighting function employed, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude. This signals that the foreground spillover shown are truly limited by intrinsic spectral features in the antenna beam patterns.

@@

This clearly demonstrates that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$. Thus, the chromaticity of antenna beam needs to be carefully controlled in EoR experiments in order to keep the foreground systematics sufficiently low.

Such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern which is independent of the position-dependent geometric delays. As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam. While delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction- and beam chromaticity-dependent effects is possible, we leave it for future work.

@@

One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument. \citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed. Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam. In this section, we provide cosmologically motivated design specifications on instrument systematics caused by these two types of reflections.

The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$-modes which are considered sensitive for EoR H{\sc i} signal detection. These delay shifts introduce ripples in the spectrum. The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the geometric phases, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for. In the Fourier domain these factors have a convolving effect. In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included.

We define the required attenuation on the reflected foreground power as the ratio: 
\begin{align}\label{eqn:attenuation}
  \Gamma_{k_\textrm{p}}(\tau) \geq \max_{|k_\parallel|>k_\textrm{p}}\left\{\frac{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)}{P_\textrm{H{\sc i}}(k_\parallel)}\right\}^{1/2},
\end{align}
where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full-band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr local sidereal time (LST) range and over both positive and negative $k_\parallel$-modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}). Thus, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$.

Both EoR models were used separately in this analysis to reduce the dependence of design specifications for reflections on any single model. However, we found similar results except for minor differences caused by small amplitude differences between the two EoR models. Hence, we only use results from using EoR model 1 at 150~MHz ($z\approx 8.47$).

\subsubsection{Reflections in Dish-Feed Assembly}\label{sec:dish-feed-reflections}

For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on a 14.6~m baseline in equation~\ref{eqn:attenuation}. Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted). These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections. It implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted). This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model. When the attenuation on dish-feed reflections is higher than these limits (outside the shaded regions), EoR will be detectable in respective $k_\parallel$-modes despite these reflections.}
\label{fig:fg-reflections-achrmbeam}
\end{figure}

@@

\subsubsection{Antenna-to-Antenna Reflections}\label{sec:antenna-antenna-reflections}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Minimum required attenuation (in dB) for antenna-to-antenna reflections to keep reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right). This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models. Regions excluding shaded regions indicate EoR will be detectable in respective $k_\parallel$-modes despite these reflections. Increase in beam chromaticity makes the requirement on attenuation more severe. For instance, $k_\parallel > 0.1\,h$~Mpc$^{-1}$ modes will be inaccessible with the simulated chromatic beam if these reflections are taken into account. However, for the same beam the instrument will have much higher tolerance despite these reflections if the modes of interest are $k_\parallel > 0.2\,h$~Mpc$^{-1}$. Due to lower chromaticity, an {\it Airy} beam offers more tolerance to reflections than the simulated chromatic beam.}
\label{fig:fg-reflections}
\end{figure*}
